\begin{tabular}{ p{1.7in} p{1.2in} p{1.5in} p{4.2in}}
{\bf Date:} & 23/02/2015 & {\bf Telescopes:} & Tele Vue 60 F6 \\ 
{\bf Time:} & 7pm-9pm & {\bf Eyepieces:} & TV Panoptic 24mm, Plossl 20mm, Nagler 7mm, Vixen SLV 5mm, Bresser 2x SA \\ 
{\bf Location:} & Cambridge, UK & {\bf Power, Exit pupil, FOV:} & 15x, 4mm, 4.30deg; 18x, 3.3mm, 2.73deg; 103x, 0.6mm, 0.77deg; 144x, 0.4mm, 0.35deg \\ 
{\bf Altitude (MAMSL):} & 12m & {\bf Filters:} & Astronomik OIII, UHC \\ 
{\bf Temperature (C):} & 1 (no wind) & & \\ 
{\bf Seeing (Antoniadi scale):} & 2 - Slight undulations & & \\ 
{\bf Transparency (AAAA scale):} & 3 - Somewhat clear & & \\ 
\end{tabular}
% Detailed observation data
\centering 
\begin{longtable}{ p{0.8in}  p{0.3in}  p{0.5in}  p{0.9in}  p{5.8in} }
\hline 
{\bf Target} & {\bf Cons} & {\bf Type} & {\bf Power} & {\bf Notes} \\ 
\hline 
M42 & Ori & CL+Neb & 15x, 18x & 4mm exit pupil + UHC shows nebula extension. OIII shows more contrast. \\ 
NGC2244 & Mon & Opn CL & 15x, 18x & Satellite cluster. Six stars in two columns  \\ 
NGC2237 & Mon & Neb & 15x, 18x & Rosette nebula. Detectable with OIII filter. Very soft grey patch. No structure. Invisible with UHC filter. \\ 
M35 & Gem & Opn CL & 15x & Detectable but not much detailed. \\ 
M36 & Aur & Opn CL & 15x & Very poor detail, but detectable.  \\ 
M37 & Aur & Opn CL & 15x & Very poor detail, but detectable.  \\ 
M38 & Aur & Opn CL & 15x & The first of the group to find. Poor detail. \\ 
M44 & Cnc & Opn CL & 15x & Praesepe. Spectactular at 15x. \\ 
M67 & Cnc & Opn CL & 15x & King cobra. Not to easy to detect. Looks like a grey patch, more visible using averted vision. \\ 
Jupiter & Cnc & Planet & 103x, 144x & A bit of wind, but the image stays crisp at high magnifications. No aberration. \\ 
NGC1662 & Ori & Opn CL & 15x, 51x & Found casually while scanning from Aldebaran to Beltegeuse. Very small little open cluster at 15x. Much better at 51x. Not easily detectable, because of its small size \\ 
NGC1647 & Tau & Opn CL & 15x  & Beautiful open cluster easily detectable from Aldebaran \\ 
NGC1746 & Tau & Opn CL & 15x & Not sure I found it. It appeared smaller than NGC1647. Possibly a darker sky reveals more interesting features. \\ 
Cr65 & Tau & Opn CL & 15x & Nice aggregation of stars, although none of them really emerges. Wide field is required. North of Orion-Meissa. \\ 
Cr70 & Ori & Opn CL & 15x & Gorgeous Orion's belt. The chain of stars surrounding Alnilam is superb. Wide field telescope. \\ 
\hline 
\end{longtable} 
